Course Project 1
==============================================================

## What is mean total number of steps taken per day?

```{r}
activity <- read.csv("activity.csv")
activity$date <- as.Date(activity$date,format="%Y-%m-%d")

sumdatadate <- setNames(aggregate(activity$steps, by=list(date=activity$date), FUN=sum, na.rm=TRUE), c("date","steps"))
hist(sumdatadate$steps, main ="Total number of steps taken per day", xlab="Number of steps",col="lightblue")
mean <- round(mean (sumdatadate$steps,na.rm = TRUE),digits=0)
mean
median <- round(median(sumdatadate$steps,na.rm = TRUE),digits=0)
median
```

## What is the average daily activity pattern?

```{r}
sumdatainterval <- setNames(aggregate(activity$steps, by=list(interval=activity$interval), FUN=mean, na.rm=TRUE), c("interval","steps"))
with(sumdatainterval,plot(steps ~ interval, type = "l",main ="Average daily activity pattern", xlab="5-minute interval ",col="blue"))
```

Let's now look at the 5-minute interval which, on average across all the days in the dataset, contains the maximum number of steps.

```{r}
max <- sumdatainterval[which.max(sumdatainterval$steps),]
max
```

## Imputing missing values

```{r}
sumna <- sum(is.na(activity$steps))
```

There are `r sumna` missing values in the dataset.

All missing values are going to be filled using the corresponding mean for that 5-minute interval.

```{r}
library(zoo)
activity2 <- activity
activity2$steps <- ave(activity2$steps, activity2$interval, FUN=na.aggregate)
sumdatadate2 <- setNames(aggregate(activity2$steps, by=list(date=activity2$date), FUN=sum, na.rm=FALSE), c("date","steps"))
hist(sumdatadate2$steps, main ="Total number of steps taken per day", xlab="Number of steps",col="lightblue")
mean2 <- round(mean (sumdatadate2$steps,na.rm = FALSE),digits=0)
mean2
median2 <- round(median (sumdatadate2$steps,na.rm = FALSE),digits=0)
median2
```

Both the mean and median number of steps taken per day are higher and very similar when imputing missing value.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
activity2$weekday=weekdays(activity2$date)
activity2$class <- ifelse(activity2$weekday %in% c("Saturday", "Sunday"), "weekend", "weekday")
activity2weekday <- subset(activity2,class=="weekday")
activity2weekend <- subset(activity2,class=="weekend")
sumdataintervalweekday <- setNames(aggregate(activity2weekday$steps, by=list(interval=activity2weekday$interval), FUN=mean, na.rm=TRUE), c("interval","steps"))
sumdataintervalweekend <- setNames(aggregate(activity2weekend$steps, by=list(interval=activity2weekend$interval), FUN=mean, na.rm=TRUE), c("interval","steps"))
par(mfrow=c(2,1), mar=c(3,2,2,2))
with(sumdataintervalweekday,plot(steps ~ interval, type = "l",main ="Weekday", xlab="5-minute interval ",col="blue"))
with(sumdataintervalweekend,plot(steps ~ interval, type = "l",main ="Weekend", xlab="5-minute interval ",col="blue"))
```


